%!TEX root = ../projecto.tex

\section{Architecture} % (fold)
\label{sec:architecture}
In this project we are going to apply Self Organizing Maps in order to detect clusters of Topics on Twitter. 
% section architecture (end)

\subsection{Data Gathering} % (fold)
 \label{sub:data_gathering}

 In order to retrieve data from Twitter, we will be using a ruby library called Twitter Stream \cite{TweetStream} , that enables the user to download and inspect the twitter stream of tweets. As the data is gathered it will be stored in a MongoDB database for posterior analyses. 
 As the twitter stream is stored, another function will interact with the twitter API in order to retrieve information from a user profile and relate him with other users by analyzing his followers and who the user is following.
 In the end of the data-gathering process it will be possible to query the database for:
 \begin{itemize}
   \item  Tweets from a user.
   \item  Query tweets for hashtag.
   \item  Query users followers and who he is following.
   \item  Query for tweets that shared the same URI 
 \end{itemize}

 Tweets will be cathegorized in:
 \begin{itemize}
   \item News Accounts
   \begin{itemize}
     \item Accounts with a lot of followers
   \end{itemize}
   \item Profile custumization 
   \item Average number of tweets a day with uri (might suggest spam)
 \end{itemize}

 % subsection data_gathering (end) 

\begin{itemize}
  \item How am I gonna solve the problem? 
  \item Describe the work that will be done 
\end{itemize}
